Classifying Human Driving Behavior via Deep Neural Networks

### 2017-05-30 paper/paper-DrexelFormat.tex
updated paper - summarized result data for ch5.1

\subsection{Resample 1 over 50}
This subsection compares results from experiments with re-sampled {\em filtered dataset} by 1 over 50. Figure \ref{fig:filter_1_50} shows average accuracy of four tests on different number of neurons in LSTM hidden layer. Table \ref{tbl:last_1_50}, Table \ref{tbl:mean_1_50}, and Table \ref{tbl:gaussian_1_50} show detail result from {\em last} method, {\em mean} method, and {\em gaussian} method respectively. Table \ref{tbl:last_1_50_time}, Table \ref{tbl:mean_1_50_time}, and Table \ref{tbl:gaussian_1_50_time} show how much time experiments took from {\em last} method, {\em mean}method, and {\em gaussian} method respectively.

The best performance was from {\em last} method with 16 number of neurons. The accuracy of this was 0.59375 (59.375\%). The worst performance was from {\em gaussian} method with 64 number of neurons. It was 0.40625 (40.625\%). Many accuracy were below 0.5 (50\%) and total average accuracy is 0.492708 (49.2708\%). The experiments with 1 over 50 re-sampled data took short time than experiments with 1 over 20 and 1 over 10 re-sampled data on later of this chapter.

\begin{figure}[t!]
    \centering
    \includegraphics[width=0.75\textwidth]{pictures/result_pictures/filtered_1_50_result.png}
    \caption{Result of 1 over 50 from {\em filtered dataset}}
    \label{fig:filter_1_50}
\end{figure}

\begin{table}[!t]
\centering
\caption{{\em last} method on 1 over 50 Re-sampled {\em filtered dataset}}
\label{tbl:last_1_50}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                              \\ \cline{3-7}
                      &                     & 16           & 32           & 64           & 128         & 256          \\ \hline
\multirow{4}{*}{1}    & 1                   & 1            & 0.5          & 0.5          & 0.75        & 0.25         \\ \cline{2-7}
                      & 2                   & 0.25         & 0.25         & 0.5          & 0.25        & 0.75         \\ \cline{2-7}
                      & 3                   & 0.75         & 0.25         & 0.25         & 0.75        & 0.75         \\ \cline{2-7}
                      & 4                   & 0.75         & 0.75         & 0.5          & 0.75        & 0.75         \\ \hline
\multirow{4}{*}{2}    & 1                   & 0.5          & 0            & 0.75         & 0.75        & 0.5          \\ \cline{2-7}
                      & 2                   & 0.25         & 0.25         & 0.5          & 0.5         & 0.25         \\ \cline{2-7}
                      & 3                   & 0.75         & 0.25         & 0.25         & 0.5         & 1            \\ \cline{2-7}
                      & 4                   & 0.5          & 0.5          & 0.75         & 0.5         & 0.5          \\ \hline
\multirow{4}{*}{3}    & 1                   & 0.5          & 0.75         & 0.5          & 0.75        & 0            \\ \cline{2-7}
                      & 2                   & 0.5          & 0.5          & 0.75         & 0.75        & 0.5          \\ \cline{2-7}
                      & 3                   & 0.5          & 0.5          & 0.25         & 0.25        & 0.5          \\ \cline{2-7}
                      & 4                   & 0.75         & 0.75         & 0.75         & 0.25        & 0.5          \\ \hline
\multirow{4}{*}{4}    & 1                   & 0.75         & 0.5          & 0.75         & 0.75        & 0.5          \\ \cline{2-7}
                      & 2                   & 0.25         & 0.5          & 0.5          & 0.25        & 0.75         \\ \cline{2-7}
                      & 3                   & 0.5          & 0.75         & 0.75         & 0.75        & 0.25         \\ \cline{2-7}
                      & 4                   & 1            & 0.75         & 0.5          & 0.5         & 0.5          \\ \hline
\multicolumn{2}{|c|}{Mean}                  & 0.59375      & 0.484375     & 0.546875     & 0.5625      & 0.515625     \\ \hline
\multicolumn{2}{|c|}{Std}                   & 0.1983000672 & 0.2536196299 & 0.1547847968 & 0.249478623 & 0.2452677109 \\ \hline
\end{tabular}
\end{table}

\begin{table}[!t]
\centering
\caption{{\em mean} method on 1 over 50 Re-sampled {\em filtered dataset}}
\label{tbl:mean_1_50}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                             \\ \cline{3-7}
                      &                     & 16          & 32           & 64          & 128          & 256          \\ \hline
\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5          & 0           & 0.25         & 0.25         \\ \cline{2-7}
                      & 2                   & 0.5         & 0.5          & 0.25        & 0.5          & 0.5          \\ \cline{2-7}
                      & 3                   & 0           & 0.75         & 0.5         & 0.25         & 0.75         \\ \cline{2-7}
                      & 4                   & 0           & 0.5          & 0.25        & 0.25         & 0.25         \\ \hline
\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5          & 0.5         & 0.5          & 0            \\ \cline{2-7}
                      & 2                   & 0.25        & 0.25         & 0.5         & 0.75         & 0.75         \\ \cline{2-7}
                      & 3                   & 0.5         & 0.5          & 0.75        & 0.5          & 0.25         \\ \cline{2-7}
                      & 4                   & 0.25        & 0.25         & 0.5         & 0.75         & 0.25         \\ \hline
\multirow{4}{*}{3}    & 1                   & 0.5         & 0.25         & 0.5         & 0.5          & 0.5          \\ \cline{2-7}
                      & 2                   & 0.25        & 0.5          & 0.75        & 0.5          & 0.25         \\ \cline{2-7}
                      & 3                   & 0.5         & 0.75         & 0.5         & 0.25         & 0.5          \\ \cline{2-7}
                      & 4                   & 0.75        & 0.5          & 0.5         & 0.75         & 0.5          \\ \hline
\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5          & 0.75        & 0.25         & 1            \\ \cline{2-7}
                      & 2                   & 0.75        & 0.75         & 0.5         & 0.25         & 0.5          \\ \cline{2-7}
                      & 3                   & 0.5         & 0.25         & 0.25        & 0.25         & 0.75         \\ \cline{2-7}
                      & 4                   & 0.5         & 0.75         & 0.75        & 0.25         & 0.75         \\ \hline
\multicolumn{2}{|c|}{Mean}                  & 0.421875    & 0.5          & 0.484375    & 0.421875     & 0.484375     \\ \hline
\multicolumn{2}{|c|}{Std}                   & 0.218303115 & 0.1825741858 & 0.213478141 & 0.1983000672 & 0.2656556355 \\ \hline
\end{tabular}
\end{table}

\begin{table}[!t]
\centering
\caption{{\em gaussian} method on 1 over 50 Re-sampled {\em filtered dataset}}
\label{tbl:gaussian_1_50}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                              \\ \cline{3-7}
                      &                     & 16           & 32           & 64           & 128         & 256          \\ \hline
\multirow{4}{*}{1}    & 1                   & 0.25         & 0.5          & 0.5          & 0.25        & 0.25         \\ \cline{2-7}
                      & 2                   & 0.75         & 0.75         & 0.25         & 0.75        & 0.5          \\ \cline{2-7}
                      & 3                   & 0.25         & 1            & 0.25         & 0.5         & 0.25         \\ \cline{2-7}
                      & 4                   & 0.5          & 0.25         & 0.25         & 0.5         & 0.75         \\ \hline
\multirow{4}{*}{2}    & 1                   & 0.75         & 0.25         & 0.5          & 0.5         & 0.5          \\ \cline{2-7}
                      & 2                   & 0.5          & 0.75         & 0.25         & 0.5         & 0.25         \\ \cline{2-7}
                      & 3                   & 0.5          & 0.5          & 0.5          & 0           & 0.25         \\ \cline{2-7}
                      & 4                   & 0.75         & 0            & 0.75         & 0.75        & 1            \\ \hline
\multirow{4}{*}{3}    & 1                   & 0.75         & 0.5          & 0.5          & 0.5         & 0.25         \\ \cline{2-7}
                      & 2                   & 0.75         & 0.25         & 0.5          & 0           & 0.5          \\ \cline{2-7}
                      & 3                   & 0.75         & 0.25         & 0.5          & 0.75        & 0.75         \\ \cline{2-7}
                      & 4                   & 0.5          & 0.25         & 0.25         & 0.75        & 0.75         \\ \hline
\multirow{4}{*}{4}    & 1                   & 0.75         & 0.5          & 0.5          & 0.75        & 0.25         \\ \cline{2-7}
                      & 2                   & 0.25         & 0.5          & 0.25         & 0.5         & 0.25         \\ \cline{2-7}
                      & 3                   & 0.75         & 0.25         & 0.5          & 0.75        & 0.5          \\ \cline{2-7}
                      & 4                   & 0.5          & 0.25         & 0.25         & 0.5         & 0.25         \\ \hline
\multicolumn{2}{|c|}{Mean}                  & 0.578125     & 0.421875     & 0.40625      & 0.515625    & 0.453125     \\ \hline
\multicolumn{2}{|c|}{Std}                   & 0.1983000672 & 0.2536196299 & 0.1547847968 & 0.249478623 & 0.2452677109 \\ \hline
\end{tabular}
\end{table}

\begin{table}[!t]
\centering
\caption{{\em last} Test Time with 1 over 50 Re-sampled {\em filtered dataset}}
\label{tbl:last_1_50_time}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurons}                                                                                                               \\ \cline{2-6}
                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
1                          & 0:18:41                      & 0:20:07                      & 0:23:00                      & 0:39:32                      & 0:54:27                      \\ \hline
2                          & 0:16:28                      & 0:18:18                      & 0:22:19                      & 0:34:39                      & 0:47:47                      \\ \hline
3                          & 0:16:25                      & 0:18:17                      & 0:22:15                      & 0:34:38                      & 0:49:43                      \\ \hline
4                          & 0:16:36                      & 0:18:28                      & 0:23:19                      & 0:34:01                      & 0:53:42                      \\ \hline
\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{0:17:03} & \multicolumn{1}{l|}{0:18:48} & \multicolumn{1}{l|}{0:22:43} & \multicolumn{1}{l|}{0:35:43} & \multicolumn{1}{l|}{0:51:25} \\ \hline
\end{tabular}
\end{table}

\begin{table}[!t]
\centering
\caption{{\em mean} Test Time with 1 over 50 Re-sampled {\em filtered dataset}}
\label{tbl:mean_1_50_time}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurons}                                                                                                               \\ \cline{2-6}
                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
1                          & 0:18:33                      & 0:19:09                      & 0:23:59                      & 0:34:57                      & 0:51:25                      \\ \hline
2                          & 0:16:25                      & 0:17:16                      & 0:22:33                      & 0:35:32                      & 0:47:26                      \\ \hline
3                          & 0:16:48                      & 0:18:07                      & 0:22:46                      & 0:34:57                      & 0:52:14                      \\ \hline
4                          & 0:16:39                      & 0:18:36                      & 0:23:23                      & 0:36:05                      & 0:51:44                      \\ \hline
\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{0:17:03} & \multicolumn{1}{l|}{0:18:48} & \multicolumn{1}{l|}{0:22:43} & \multicolumn{1}{l|}{0:35:43} & \multicolumn{1}{l|}{0:51:25} \\ \hline
\end{tabular}
\end{table}

\begin{table}[!t]
\centering
\caption{{\em gaussian} Test Time with 1 over 50 Re-sampled {\em filtered dataset}}
\label{tbl:gaussian_1_50_time}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurons}                                                                                                               \\ \cline{2-6}
                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
1                          & 0:18:05                      & 0:18:33                      & 0:22:40                      & 0:37:31                      & 0:54:11                      \\ \hline
2                          & 0:16:24                      & 0:18:08                      & 0:22:19                      & 0:35:22                      & 0:48:40                      \\ \hline
3                          & 0:16:17                      & 0:18:00                      & 0:22:18                      & 0:35:12                      & 0:53:03                      \\ \hline
4                          & 0:16:28                      & 0:18:39                      & 0:22:33                      & 0:34:25                      & 0:54:57                      \\ \hline
\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{0:16:49} & \multicolumn{1}{l|}{0:18:20} & \multicolumn{1}{l|}{0:22:28} & \multicolumn{1}{l|}{0:35:38} & \multicolumn{1}{l|}{0:52:43} \\ \hline
\end{tabular}
\end{table}

\subsection{Resample 1 over 20}
This subsection compares results from experiments with re-sampled {\em filtered dataset} by 1 over 20. Figure \ref{fig:filter_1_20} shows the average accuracy of four tests on different number of neurons in LSTM hidden layer. Table \ref{tbl:last_1_20}, Table \ref{tbl:mean_1_20}, and Table \ref{tbl:gaussian_1_20} show a detailed result from {\em last} method, {\em mean} method, and {\em gaussian} method respectively. Table \ref{tbl:last_1_20_time}, Table \ref{tbl:mean_1_20_time}, and Table \ref{tbl:gaussian_1_20_time} show how much time experiments took from {\em last} method, {\em mean}method, and {\em gaussian} method respectively.

The best performance was from {\em mean} method with 32 and 256 number of neurons. The accuracy of this was 0.59375 (59.375\%) as same as best performance from experiments with 1 over 50 re-sampled data. The worst performance was also from {\em mean} method with 128 number of neurons. It was 0.375 (37.5\%), which was worse than the worst performance from experiments with 1 over 50 re-sampled data. However, the total average was 0.515625 (51.5625\%) which was slightly higher than the total average 0.492708 (49.2708\%) from experiments with 1 over 50 re-sampled data because size of 1 over 20 re-sampled data is 2.5 times more than size of 1 over 50 re-sampled data. More amount of data also affected the test time. Even size of the data is 2.5 times more, the test time took more than 2.5 times than the test time from experiments with 1 over 50 re-sampled data.

\begin{figure}[t!]
    \centering
    \includegraphics[width=0.75\textwidth]{pictures/result_pictures/filtered_1_20_result.png}
    \caption{Result of 1 over 20 from {\em filtered dataset}}
    \label{fig:filter_1_20}
\end{figure}

\begin{table}[!t]
\centering
\caption{{\em last} method on 1 over 20 Re-sampled {\em filtered dataset}}
\label{tbl:last_1_20}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                             \\ \cline{3-7}
                      &                     & 16           & 32           & 64          & 128         & 256          \\ \hline
\multirow{4}{*}{1}    & 1                   & 0.75         & 0.5          & 0.25        & 0.5         & 0.5          \\ \cline{2-7}
                      & 2                   & 0.5          & 0.25         & 0.75        & 0.5         & 0.5          \\ \cline{2-7}
                      & 3                   & 0.5          & 0.25         & 0.5         & 0.5         & 0.25         \\ \cline{2-7}
                      & 4                   & 0.5          & 0.25         & 0.75        & 0.25        & 0.5          \\ \hline
\multirow{4}{*}{2}    & 1                   & 0.25         & 1            & 0.25        & 0.5         & 0            \\ \cline{2-7}
                      & 2                   & 0.5          & 0.25         & 0.5         & 0.5         & 0.75         \\ \cline{2-7}
                      & 3                   & 0.5          & 0.25         & 0.5         & 0.5         & 0.5          \\ \cline{2-7}
                      & 4                   & 0.5          & 0.5          & 0.25        & 0.25        & 0.25         \\ \hline
\multirow{4}{*}{3}    & 1                   & 0.25         & 0.75         & 0.5         & 0.5         & 0.5          \\ \cline{2-7}
                      & 2                   & 0.25         & 0            & 0.75        & 0.5         & 0.5          \\ \cline{2-7}
                      & 3                   & 0.5          & 0.5          & 0.5         & 0.75        & 0.75         \\ \cline{2-7}
                      & 4                   & 0.25         & 0.5          & 0.5         & 0.25        & 0.75         \\ \hline
\multirow{4}{*}{4}    & 1                   & 0.75         & 0.5          & 0.5         & 0.25        & 0.5          \\ \cline{2-7}
                      & 2                   & 0.25         & 0.75         & 1           & 0.75        & 0.25         \\ \cline{2-7}
                      & 3                   & 0.75         & 0.75         & 0.25        & 0.75        & 1            \\ \cline{2-7}
                      & 4                   & 0.75         & 0.25         & 0.5         & 1           & 0.5          \\ \hline
\multicolumn{2}{|c|}{Mean}                  & 0.484375     & 0.453125     & 0.515625    & 0.515625    & 0.5          \\ \hline
\multicolumn{2}{|c|}{Std}                   & 0.1929756029 & 0.2617051458 & 0.213478141 & 0.213478141 & 0.2415229458 \\ \hline
\end{tabular}
\end{table}

>>>>

\subsection{Resample 1 over 50}
This subsection compares results from experiments with 1 over 50 re-sampled {\em filtered dataset} by {\em last}, {\em mean}, and {\em gaussian} methods. Each dataset were tested four times with different number of neurons in LSTM hidden layer: 16, 32, 64, 128, and 256 neurons. Figure \ref{fig:filter_1_50} shows average accuracy from four tests on different number of neurons. Table \ref{tbl:filtered_avg_1_50} shows average accuracy of four tests on different number of neurons, Table \ref{tbl:filtered_std_1_50} shows standard deviation of four tests on different number of neurons, and Table \ref{tbl:filtered_time_1_50} shows test time of four tests on different number of neurons.

The best performance was from {\em last} method with 16 number of neurons. The accuracy of this was 0.59375 (59.375\%). The worst performance was from {\em gaussian} method with 64 number of neurons. It was 0.40625 (40.625\%). Test with 64 neurons gave most stable result because standard deviation of this was the smallest. Many accuracy were below 0.5 (50\%) and total average accuracy is 0.492708 (49.2708\%). The experiments with 1 over 50 re-sampled data took short time than experiments with 1 over 20 and 1 over 10 re-sampled data on later of this chapter.

\begin{figure}[t!]
    \centering
    \includegraphics[width=0.75\textwidth]{pictures/result_pictures/filtered_1_50_result.png}
    \caption{Result of 1 over 50 Re-sampled {\em filtered dataset}}
    \label{fig:filter_1_50}
\end{figure}

\begin{table}[!t]
\centering
\caption{Average Accuracy of Result from 1 over 50 Re-sampled {\em filtered dataset}}
\label{tbl:filtered_avg_1_50}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}1 over 50\\ Average\end{tabular}} & \multicolumn{5}{c|}{The number of neurons}               \\ \cline{2-6} 
                                                                             & 16       & 32       & 64           & 128      & 256      \\ \hline
\textit{last}                                                                & 0.59375  & 0.484375 & 0.546875     & 0.5625   & 0.515625 \\ \hline
\textit{mean}                                                                & 0.421875 & 0.5      & 0.484375     & 0.421875 & 0.484375 \\ \hline
\textit{gaussian}                                                            & 0.578125 & 0.421875 & 0.40625      & 0.515625 & 0.453125 \\ \hline
Average                                                                      & 0.53125  & 0.46875  & 0.4791666667 & 0.5      & 0.484375 \\ \hline
\end{tabular}
\end{table}

\begin{table}[!t]
\centering
\caption{Standard Deviation of Result from 1 over 50 Re-sampled {\em filtered dataset}}
\label{tbl:filtered_std_1_50}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}1 over 50\\ Std.\end{tabular}} & \multicolumn{5}{c|}{The number of neurons}                               \\ \cline{2-6} 
                                                                          & 16           & 32           & 64           & 128          & 256          \\ \hline
\textit{last}                                                             & 0.1983000672 & 0.2536196299 & 0.1547847968 & 0.249478623  & 0.2452677109 \\ \hline
\textit{mean}                                                             & 0.218303115  & 0.1825741858 & 0.213478141  & 0.1983000672 & 0.2656556355 \\ \hline
\textit{gaussian}                                                         & 0.1983000672 & 0.2536196299 & 0.1547847968 & 0.249478623  & 0.2452677109 \\ \hline
Average                                                                   & 0.2049677498 & 0.2299378152 & 0.1743492449 & 0.2324191044 & 0.2520636858 \\ \hline
\end{tabular}
\end{table}

\begin{table}[!t]
\centering
\caption{Test Time from 1 over 50 Re-sampled {\em filtered dataset}}
\label{tbl:filtered_time_1_50}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}1 over 50\\ Time\end{tabular}} & \multicolumn{5}{c|}{The number of neurons}      \\ \cline{2-6} 
                                                                          & 16      & 32      & 64      & 128     & 256     \\ \hline
\textit{last}                                                             & 0:17:03 & 0:18:48 & 0:22:43 & 0:35:43 & 0:51:25 \\ \hline
\textit{mean}                                                             & 0:17:06 & 0:18:17 & 0:23:10 & 0:35:23 & 0:50:42 \\ \hline
\textit{gaussian}                                                         & 0:16:49 & 0:18:20 & 0:22:28 & 0:35:38 & 0:52:43 \\ \hline
Average                                                                   & 0:16:59 & 0:18:28 & 0:22:47 & 0:35:35 & 0:51:37 \\ \hline
\end{tabular}
\end{table}

%\begin{table}[!t]
%\centering
%\caption{{\em last} method on 1 over 50 Re-sampled {\em filtered dataset}}
%\label{tbl:last_1_50}
%\begin{tabular}{|c|c|c|c|c|c|c|}
%\hline
%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                              \\ \cline{3-7}
%                      &                     & 16           & 32           & 64           & 128         & 256          \\ \hline
%\multirow{4}{*}{1}    & 1                   & 1            & 0.5          & 0.5          & 0.75        & 0.25         \\ \cline{2-7}
%                      & 2                   & 0.25         & 0.25         & 0.5          & 0.25        & 0.75         \\ \cline{2-7}
%                      & 3                   & 0.75         & 0.25         & 0.25         & 0.75        & 0.75         \\ \cline{2-7}
%                      & 4                   & 0.75         & 0.75         & 0.5          & 0.75        & 0.75         \\ \hline
%\multirow{4}{*}{2}    & 1                   & 0.5          & 0            & 0.75         & 0.75        & 0.5          \\ \cline{2-7}
%                      & 2                   & 0.25         & 0.25         & 0.5          & 0.5         & 0.25         \\ \cline{2-7}
%                      & 3                   & 0.75         & 0.25         & 0.25         & 0.5         & 1            \\ \cline{2-7}
%                      & 4                   & 0.5          & 0.5          & 0.75         & 0.5         & 0.5          \\ \hline
%\multirow{4}{*}{3}    & 1                   & 0.5          & 0.75         & 0.5          & 0.75        & 0            \\ \cline{2-7}
%                      & 2                   & 0.5          & 0.5          & 0.75         & 0.75        & 0.5          \\ \cline{2-7}
%                      & 3                   & 0.5          & 0.5          & 0.25         & 0.25        & 0.5          \\ \cline{2-7}
%                      & 4                   & 0.75         & 0.75         & 0.75         & 0.25        & 0.5          \\ \hline
%\multirow{4}{*}{4}    & 1                   & 0.75         & 0.5          & 0.75         & 0.75        & 0.5          \\ \cline{2-7}
%                      & 2                   & 0.25         & 0.5          & 0.5          & 0.25        & 0.75         \\ \cline{2-7}
%                      & 3                   & 0.5          & 0.75         & 0.75         & 0.75        & 0.25         \\ \cline{2-7}
%                      & 4                   & 1            & 0.75         & 0.5          & 0.5         & 0.5          \\ \hline
%\multicolumn{2}{|c|}{Mean}                  & 0.59375      & 0.484375     & 0.546875     & 0.5625      & 0.515625     \\ \hline
%\multicolumn{2}{|c|}{Std}                   & 0.1983000672 & 0.2536196299 & 0.1547847968 & 0.249478623 & 0.2452677109 \\ \hline
%\end{tabular}
%\end{table}
%
%\begin{table}[!t]
%\centering
%\caption{{\em mean} method on 1 over 50 Re-sampled {\em filtered dataset}}
%\label{tbl:mean_1_50}
%\begin{tabular}{|c|c|c|c|c|c|c|}
%\hline
%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                             \\ \cline{3-7}
%                      &                     & 16          & 32           & 64          & 128          & 256          \\ \hline
%\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5          & 0           & 0.25         & 0.25         \\ \cline{2-7}
%                      & 2                   & 0.5         & 0.5          & 0.25        & 0.5          & 0.5          \\ \cline{2-7}
%                      & 3                   & 0           & 0.75         & 0.5         & 0.25         & 0.75         \\ \cline{2-7}
%                      & 4                   & 0           & 0.5          & 0.25        & 0.25         & 0.25         \\ \hline
%\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5          & 0.5         & 0.5          & 0            \\ \cline{2-7}
%                      & 2                   & 0.25        & 0.25         & 0.5         & 0.75         & 0.75         \\ \cline{2-7}
%                      & 3                   & 0.5         & 0.5          & 0.75        & 0.5          & 0.25         \\ \cline{2-7}
%                      & 4                   & 0.25        & 0.25         & 0.5         & 0.75         & 0.25         \\ \hline
%\multirow{4}{*}{3}    & 1                   & 0.5         & 0.25         & 0.5         & 0.5          & 0.5          \\ \cline{2-7}
%                      & 2                   & 0.25        & 0.5          & 0.75        & 0.5          & 0.25         \\ \cline{2-7}
%                      & 3                   & 0.5         & 0.75         & 0.5         & 0.25         & 0.5          \\ \cline{2-7}
%                      & 4                   & 0.75        & 0.5          & 0.5         & 0.75         & 0.5          \\ \hline
%\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5          & 0.75        & 0.25         & 1            \\ \cline{2-7}
%                      & 2                   & 0.75        & 0.75         & 0.5         & 0.25         & 0.5          \\ \cline{2-7}
%                      & 3                   & 0.5         & 0.25         & 0.25        & 0.25         & 0.75         \\ \cline{2-7}
%                      & 4                   & 0.5         & 0.75         & 0.75        & 0.25         & 0.75         \\ \hline
%\multicolumn{2}{|c|}{Mean}                  & 0.421875    & 0.5          & 0.484375    & 0.421875     & 0.484375     \\ \hline
%\multicolumn{2}{|c|}{Std}                   & 0.218303115 & 0.1825741858 & 0.213478141 & 0.1983000672 & 0.2656556355 \\ \hline
%\end{tabular}
%\end{table}
%
%\begin{table}[!t]
%\centering
%\caption{{\em gaussian} method on 1 over 50 Re-sampled {\em filtered dataset}}
%\label{tbl:gaussian_1_50}
%\begin{tabular}{|c|c|c|c|c|c|c|}
%\hline
%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                              \\ \cline{3-7}
%                      &                     & 16           & 32           & 64           & 128         & 256          \\ \hline
%\multirow{4}{*}{1}    & 1                   & 0.25         & 0.5          & 0.5          & 0.25        & 0.25         \\ \cline{2-7}
%                      & 2                   & 0.75         & 0.75         & 0.25         & 0.75        & 0.5          \\ \cline{2-7}
%                      & 3                   & 0.25         & 1            & 0.25         & 0.5         & 0.25         \\ \cline{2-7}
%                      & 4                   & 0.5          & 0.25         & 0.25         & 0.5         & 0.75         \\ \hline
%\multirow{4}{*}{2}    & 1                   & 0.75         & 0.25         & 0.5          & 0.5         & 0.5          \\ \cline{2-7}
%                      & 2                   & 0.5          & 0.75         & 0.25         & 0.5         & 0.25         \\ \cline{2-7}
%                      & 3                   & 0.5          & 0.5          & 0.5          & 0           & 0.25         \\ \cline{2-7}
%                      & 4                   & 0.75         & 0            & 0.75         & 0.75        & 1            \\ \hline
%\multirow{4}{*}{3}    & 1                   & 0.75         & 0.5          & 0.5          & 0.5         & 0.25         \\ \cline{2-7}
%                      & 2                   & 0.75         & 0.25         & 0.5          & 0           & 0.5          \\ \cline{2-7}
%                      & 3                   & 0.75         & 0.25         & 0.5          & 0.75        & 0.75         \\ \cline{2-7}
%                      & 4                   & 0.5          & 0.25         & 0.25         & 0.75        & 0.75         \\ \hline
%\multirow{4}{*}{4}    & 1                   & 0.75         & 0.5          & 0.5          & 0.75        & 0.25         \\ \cline{2-7}
%                      & 2                   & 0.25         & 0.5          & 0.25         & 0.5         & 0.25         \\ \cline{2-7}
%                      & 3                   & 0.75         & 0.25         & 0.5          & 0.75        & 0.5          \\ \cline{2-7}
%                      & 4                   & 0.5          & 0.25         & 0.25         & 0.5         & 0.25         \\ \hline
%\multicolumn{2}{|c|}{Mean}                  & 0.578125     & 0.421875     & 0.40625      & 0.515625    & 0.453125     \\ \hline
%\multicolumn{2}{|c|}{Std}                   & 0.1983000672 & 0.2536196299 & 0.1547847968 & 0.249478623 & 0.2452677109 \\ \hline
%\end{tabular}
%\end{table}

%\begin{table}[!t]
%\centering
%\caption{{\em last} Test Time with 1 over 50 Re-sampled {\em filtered dataset}}
%\label{tbl:last_1_50_time}
%\begin{tabular}{|c|c|c|c|c|c|}
%\hline
%\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurons}                                                                                                               \\ \cline{2-6}
%                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
%1                          & 0:18:41                      & 0:20:07                      & 0:23:00                      & 0:39:32                      & 0:54:27                      \\ \hline
%2                          & 0:16:28                      & 0:18:18                      & 0:22:19                      & 0:34:39                      & 0:47:47                      \\ \hline
%3                          & 0:16:25                      & 0:18:17                      & 0:22:15                      & 0:34:38                      & 0:49:43                      \\ \hline
%4                          & 0:16:36                      & 0:18:28                      & 0:23:19                      & 0:34:01                      & 0:53:42                      \\ \hline
%\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{0:17:03} & \multicolumn{1}{l|}{0:18:48} & \multicolumn{1}{l|}{0:22:43} & \multicolumn{1}{l|}{0:35:43} & \multicolumn{1}{l|}{0:51:25} \\ \hline
%\end{tabular}
%\end{table}
%
%\begin{table}[!t]
%\centering
%\caption{{\em mean} Test Time with 1 over 50 Re-sampled {\em filtered dataset}}
%\label{tbl:mean_1_50_time}
%\begin{tabular}{|c|c|c|c|c|c|}
%\hline
%\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurons}                                                                                                               \\ \cline{2-6}
%                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
%1                          & 0:18:33                      & 0:19:09                      & 0:23:59                      & 0:34:57                      & 0:51:25                      \\ \hline
%2                          & 0:16:25                      & 0:17:16                      & 0:22:33                      & 0:35:32                      & 0:47:26                      \\ \hline
%3                          & 0:16:48                      & 0:18:07                      & 0:22:46                      & 0:34:57                      & 0:52:14                      \\ \hline
%4                          & 0:16:39                      & 0:18:36                      & 0:23:23                      & 0:36:05                      & 0:51:44                      \\ \hline
%\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{0:17:03} & \multicolumn{1}{l|}{0:18:48} & \multicolumn{1}{l|}{0:22:43} & \multicolumn{1}{l|}{0:35:43} & \multicolumn{1}{l|}{0:51:25} \\ \hline
%\end{tabular}
%\end{table}
%
%\begin{table}[!t]
%\centering
%\caption{{\em gaussian} Test Time with 1 over 50 Re-sampled {\em filtered dataset}}
%\label{tbl:gaussian_1_50_time}
%\begin{tabular}{|c|c|c|c|c|c|}
%\hline
%\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurons}                                                                                                               \\ \cline{2-6}
%                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
%1                          & 0:18:05                      & 0:18:33                      & 0:22:40                      & 0:37:31                      & 0:54:11                      \\ \hline
%2                          & 0:16:24                      & 0:18:08                      & 0:22:19                      & 0:35:22                      & 0:48:40                      \\ \hline
%3                          & 0:16:17                      & 0:18:00                      & 0:22:18                      & 0:35:12                      & 0:53:03                      \\ \hline
%4                          & 0:16:28                      & 0:18:39                      & 0:22:33                      & 0:34:25                      & 0:54:57                      \\ \hline
%\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{0:16:49} & \multicolumn{1}{l|}{0:18:20} & \multicolumn{1}{l|}{0:22:28} & \multicolumn{1}{l|}{0:35:38} & \multicolumn{1}{l|}{0:52:43} \\ \hline
%\end{tabular}
%\end{table}

\subsection{Resample 1 over 20}
This subsection compares results from experiments with 1 over 20 re-sampled {\em filtered dataset} by {\em last}, {\em mean}, and {\em gaussian} methods. Each dataset were tested four times with different number of neurons in LSTM hidden layer: 16, 32, 64, 128, and 256 neurons. Figure \ref{fig:filter_1_20} shows average accuracy from four tests on different number of neurons. Table \ref{tbl:filtered_avg_1_20} shows average accuracy of four tests on different number of neurons, Table \ref{tbl:filtered_std_1_20} shows standard deviation of four tests on different number of neurons, and Table \ref{tbl:filtered_time_1_20} shows test time of four tests on different number of neurons.
